Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-10 Response to reviewers.tex

\noindent (1) \emph{Generally speaking, predicting sales is regarded as a regression problem (numerical output) rather than classification (categorical one). Both CFS and RelieFF are originally designed for classification problem. When CFS is used for regression, please to introduce how to estimate correlations between each feature and output (total sales). Since RReliefF, as a variant of ReliefF, is special for regression, why do not the authors use RReliefF? }

\begin{verbatim}
In all our experiments we have applied  WEKA's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [73] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph) 
\begin{verbatim}
For CSF, estimating the correlation between attributes is 
standard linear (Pearson's) correlation. The details have 
been added to the text to clarify this point.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph)

~\\
\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?}

\begin{verbatim}
The current paper includes in sub-section 4.2 six methods: M5P, kNN, 
RF, LR, SVM, MLP, and ELM (requested by Reviewer #2). After having 
included ELM, new references have been added (the list of new 
references can be found at the end of this letter).

Moreover, as suggested by Reviewer #2 (see his/her first comment), 
the results obtained with the last two methods have been included and 
analyzed in this new version of the paper.
\end{verbatim}
% Antonio - TODO: say where are these results (table/figure/page)
% where (finally) are we going to put those subsections?   XD

@@

~\\
\noindent (2) \emph{For RF, how many trees are set? }

\begin{verbatim}
As far as the number of trees is concerned, in the experiments 
section, when describing the parameter settings, 
it has been mentioned that the best performance was obtained 
with a number of trees equal to 50.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph)

~\\
\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure. That is, some features are chosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The aim is simply to show to the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.

This has been clarified in the text with the following sentence, at the end of section 5.2 (page XX):

"It is important to note that both RF and M5P have an embedded feature selection mechanism (the variables which compose the final trees), however this is part of their inherent procedure. In the following section we will apply three filter-based feature selection techniques on the dataset, so all the methods will profit."

\end{verbatim}
% Antonio - TODO: Put the number of page.

@@

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
The reviewer is right, thus, we have revised the whole paper remarking 
the regression topic present on the work. We have clarified in several
 paragraphs that the problem has been addressed by means of regression 
methods (for instance, note the new title of Section 4.2), or we have 
generally referred to the term `regression' instead of `classification', 
in order to better suit the regression viewpoint.

Moreover this suggestion have been also addressed solving the issue 
related to comment #1, where the application procedure of feature 
selection methods for regression problems has been clarified. 
\end{verbatim}

@@

~\\
\noindent (5) \emph{It is necessary to write that paper more concisely. }

\begin{verbatim}
Following reviewer's suggestion we have reorganized some parts 
of the text, removed some sentences, and rewritten several paragraphs 
in order to avoid repetition, and also to make them shorter, clearer, 
and easier to comprehend.

@@

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#2}

\noindent \emph{This paper applies some machine learning technologies to address issues related to book sales. There are some revisions that should be addressed by authors: } \\

\noindent (1) \emph{The ANN and ELM (extreme learning machine) should be added into the experiments; }

\begin{verbatim}
Following the reviewer's request, we have conducted several new experiments 
and added the results of ANN (MLP) and ELM to Tables XX, YY, ZZ and
Figures AA, BB accordingly. 
Their results have been also analyzed with the rest of methods, in the 
paragraphs related to each one of the new figures.
A description of both approaches have been also included in subsection 4.2.

@@

In addition new references have been added to the paper, related to these 
methods, namely [REF_XX, REF_YY]. In any case, the list of new references
can be found at the end of this letter.
\end{verbatim}
% Antonio - TODO: Complete with the number of tables and figures, along with the new references

~\\
\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}

\begin{verbatim}
Following reviewer's request, we have rewritten the introduction and 
included new paragraphs to better explain the problem and the aim of 
the paper. In addition, we have laid out our methodology to differentiate 
it from other approaches.

We have also remarked the contribution with the paragraphs (see page XX):

"Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how 
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a company that sells
software for publishers, we analyse them and compute predictive models 
that can be mainly used as decision-aid tools for book publishers. With 
these models, publishers will be able to combine their expert knowledge 
about the market with the created forecasting models in order to get a 
reliable estimation of book sales, and, based on it, act consequently 
in order to maximize the books sold for a particular print run.

This will improve the current decision flow that the publishers follow, 
which consist in analysing (in a subjective way) the quality of the book 
and its features (author, genre, etc), and take a `fuzzy' decision roughly
 between printing 300 copies (standard book) or 5000 (best seller).

This process might be tedious, especially when the amount of data is quite
 large. Moreover, different experts can reach different predictions from 
the same dataset [4].

With these issues in mind, in this paper, we firstly present an 
analysis on a real dataset, provided by the Spanish publishing company 
Trevenque Editorial S.L.
This study has been conducted by means of data mining and visualisation
 techniques. Then, a feature selection process is performed using three
 different methods, in order to find out what are the relevant variables
 describing a book  in the prediction, or estimation, procedure. 
This procedure is performed by applying a set of regression algorithms 
to the different datasets (those with a different number of variables), 
yielding a set of models which could be used as the desired tool.

Given this, the main contribution of this paper to the state of the art 
is the development of the aforementioned methodology to process book sales 
data, in which: firstly, the most relevant variables are identified, and then,
 these variables are considered to `refine' the data in order to conduct
 accurate predictions on future sales. To our knowledge this is the first 
work in which regression methods have been applied to estimate sales for 
new launched books. Moreover, as stated before, we have used in the study 
a real dataset of book sales (related to the Spanish market), which is 
another point to remark."

\end{verbatim}
% TODO: update with the correct page where those paragraphs can be found

@@

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommendation 
systems have been added to the future work section, at the end 
of Section 7 (see page XX).
\end{verbatim}
% Antonio - TODO: put the correct page when the text is finished

~\\
\noindent (4) \emph{Some tables should be transfer to figures because there are too many tables. }

\begin{verbatim}
Following reviewer's suggestion, all the results tables have been 
moved to the Appendix and that data has been summarized and 
presented as the new Figures XX, YY, ZZ in order to make that numeric 
data clearer and to improve their comprehension.

Their analysis has been also changed and improved considering Figures 
instead of tables.
\end{verbatim}
% Antonio - TODO: put the correct page when the text is finished

@@

%------------------------------------------------------------------------------------
\section{Comments by Reviewer \#3}

\noindent \emph{There are several concerns should be considered.}\\

\noindent (1) \emph{In section introduction, this manuscript should describe the contribution of this work. }

\begin{verbatim}
The reviewer is right. The main contribution of this paper to the 
state of the art was not properly described. Thus, as stated above 
in the second response to Reviewer #2, we have clarified this in 
the introduction improving some paragraphs and adding new sentences 
(see page XX):

"Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how 
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a company that sells
software for publishers, we analyse them and compute predictive models 
that can be mainly used as decision-aid tools for book publishers. With 
these models, publishers will be able to combine their expert knowledge 
about the market with the created forecasting models in order to get a 
reliable estimation of book sales, and, based on it, act consequently 
in order to maximize the books sold for a particular print run.

This will improve the current decision flow that the publishers follow, 
which consist in analysing (in a subjective way) the quality of the book 
and its features (author, genre, etc), and take a `fuzzy' decision roughly
 between printing 300 copies (standard book) or 5000 (best seller).

This process might be tedious, especially when the amount of data is quite
 large. Moreover, different experts can reach different predictions from 
the same dataset [4].

With these issues in mind, in this paper, we firstly present an 
analysis on a real dataset, provided by the Spanish publishing company 
Trevenque Editorial S.L.
This study has been conducted by means of data mining and visualisation
 techniques. Then, a feature selection process is performed using three
 different methods, in order to find out what are the relevant variables
 describing a book  in the prediction, or estimation, procedure. 
This procedure is performed by applying a set of regression algorithms 
to the different datasets (those with a different number of variables), 
yielding a set of models which could be used as the desired tool.

Given this, the main contribution of this paper to the state of the art 
is the development of the aforementioned methodology to process book sales 
data, in which: firstly, the most relevant variables are identified, and then,
 these variables are considered to `refine' the data in order to conduct
 accurate predictions on future sales. To our knowledge this is the first 
work in which regression methods have been applied to estimate sales for 
new launched books. Moreover, as stated before, we have used in the study 
a real dataset of book sales (related to the Spanish market), which is 
another point to remark."

\end{verbatim}

@@

~\\
\noindent (2) \emph{sections 4.1 and 4.2 should be moved to section 2. }

\begin{verbatim}
Although the reviewer is right, considering that those sections describe 
methods and metrics used in the state of the art, the authors wanted to 
have section 2 as independent from the rest, given it is a key section on 
every work.

The authors think that `mixing' background concepts there could mean, 
somehow, a lost in quality for that section.

In addition, we also guess that if those subsections would be moved 
to section 2, maybe section 4.3 should be moved too, as it also describes 
some background concepts (usual evaluation metrics). Thus, the methodology 
section would be certainly quite short.

Finally, the rest of the reviewers haven't requested to change the 
organisation and, moreover, Reviewer #2 has remarked that the paper 
is well organized in his/her last comment.

For these reasons we have decided to maintain those as subsections 
of methodology (section 4).

We hope that the reviewer agrees with this decision.
\end{verbatim}
% Antonio - TODO - check this answer for not doing nothing. XD
% Well, actually I have to undo several things. :(

@@

~\\
\noindent (3) \emph{In section 4, this manuscript should show a flowchart of the proposed forecasting scheme and describe it. }

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology including a flowchart (see Figure XX 
at page YY).

Every step/stage shown in that figure has been described in the 
following paragraphs.
\end{verbatim}

@@

~\\
\noindent (4) \emph{In Section 5, parameter settings of 
M5P, kNN and RF also should be shown. }

\begin{verbatim}
Reviewer is right, so we have improved Section 5, including the 
parameter settings of M5P, kNN and RF methods (see paragraph XX at 
page YY), along with the configuration parameters for the rest of 
methods.

The authors want to express our gratitude to this reviewer 
for his/her valuable comments and suggestions.
\end{verbatim}
% Antonio - TODO: say paragraph/page where they are.

### 2016-09-10 paper.tex
Finishing all
But the final revision and 'Gingerization'. XD

Closes #54
Closes #56

Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a company that sells
software for publishers, we analyse them and compute predictive models that can be mainly used as decision-aid tools for book publishers. With these models, publishers will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book
sales, and, based on it, act consequently in order to maximize the books sold for a particular print run. This will improve the current decision flow that the publishers follow, which consist in analysing (in a subjective way) the quality of the book and its features (author, genre, etc), and take a `fuzzy' decision roughly between printing 300 copies (standard book) or 5000 (best seller).

Our main contribution is, thus, the development of the methodology to process book sales data in order to find out relevant variables, and then, use these variables to process the data to accurately estimate future sales. To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books. Moreover, we have considered a real dataset of book sales (related to the Spanish market), which is another point to remark.

Therefore, in this paper, the problem of predicting total sales is approached using real data provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. This company offers management systems and services for bookshops, publishers, and distributors. 
% (Paloma) From here:
Usually, the company's expert sales managers analysed historical data
and applied their knowledge on external variables to compute correct
estimations (predictions); for instance, they can decide increasing or
decreasing the sales forecast based on season or sales period. 
Nevertheless, just carrying out the analysis and forecasting process
as a human expert may lead to imprecise predictions, and they may not
take all the variables into account.  
% (Paloma) to here, is repeating all over again the process of deciding how many books to print. I think this paragraph should be unified somehow with the previous explanations and to re-order, because the previous paragraph seems like the end of the introduction, but then we go deep in the explanations again... It's not an easy read :(
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

With this issue in mind, in this paper we firstly present an analysis
on the aforementioned real dataset, by means of data mining and
visualisation techniques. Then, a feature selection process is
conducted using three different methods, in order to find out what are
the relevant variables describing a book in the prediction (or
regression) procedure. 
% (Paloma) Why brackets? Suggestions:
% relevant variables describing a book in the prediction or regression procedure
% relevant variables describing a book in the prediction, or regression, procedure
% relevant variables describing a book in the prediction (regression) procedure <- here brackets are ok (me thinks)
After this, a forecasting stage is performed
applying a set of regression algorithms to the different datasets,
also considering a different number of variables. 
The value of this methodology is contrasted considering four different
publishing companies being representative as top sellers, mid-range
sellers, the most varied, and one which sells a medium amount of
different books. From this, we draw insight on what are the important
factors when selling a book and some rule of thumbs extracted from the
prediction methods.

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes, and shows a set of definitions of the regression methods applied in the paper as well as the evaluation metrics considered.
Then, Section \ref{sec:problem} introduces the problem of the estimation of print-run
% (Paloma) Guys, 'print run' is written a total of 28 times:
% 23 are in the 'print-run' form
% 5 are 'print-run' (with a dash), of which one is inside the list of variables. But what about the rest inside text? Shouldn't they go ALL either with or without the dash?
for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study.  These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies. Obtained results for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

Thus, taking into account the kind of problem we address in this
paper, i.e. the prediction of sales of a new product for which no
historical data are available, the classical forecasting methods based
on time-series are not adequate, although they can obviously be used once 
the book has been launched for sale. 
In our work the relevant variables in the prediction of sales are identified
by means of data visualisation and feature selection methods. 
Then, machine learning techniques are applied to predict sales and to infer 
the ideal print-run of a book.
In addition, since publishers need models to explain obtained predictions, 
`black box' forecasting methods may not be suitable, so models based
on decision rules have been tested as an alternative.

% following two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)

Many of these previous papers propose using different prediction methods to find out which one performs the best.
Thus, next subsections describe several forecasting methods and different 
evaluation metrics, commonly used in the bibliography that have been chosen 
to address the problem of book sales prediction.

%-------------------------------------------------
\subsection{Regression methods}
\label{subsec:select_method}

As previously stated, there are many prediction methods available in the 
literature, each one with a different parameter set that may affect the 
obtained results.

@@

%-------------------------------------------------
\subsection{Models evaluation}
\label{subsec:models_evaluation}

@@

\begin{minipage}{2.45in}\begin{small}
 \begin{verbatim}
reference
author
retail price
subject1
subject2
subject3
publisher
collection
bookbinding
print-run
total sales
dept stores sales
sales through delegates
rest of sales
total sales 1st year
mall sales 1st year
delegates sales 1st year
rest of sales 1st year
total distributed
distributed through dept stores
distributed through delegates
distributed - rest
total distributed 1st year
distrib. through dept stores 1st year
distrib. through delegates 1st year
\end{verbatim}
\end{small} \end{minipage}     &

Therefore, after the data has been collected and initially preprocessed (as described in the previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.

FS methods check the relevance of all the variables of the patterns, aiming to reduce the set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
This task may also help to identify leading indicators to be considered 
by a human expert to make predictions.
At this stage of the methodology, both numerical and visualisation-based approaches have been applied, in order to select the best set of variables for the forecasting methods.

After this process has been conducted, different prediction methods have been applied on the dataset. These methods have been described in Section \ref{subsec:select_method}, and include rule- and tree-based algorithms, together with numerical regression methods.

As a result, several prediction models are obtained. Then the obtained models for the whole dataset have been evaluated by means of the metrics described in Section \ref{subsec:models_evaluation}. The results are presented in Section \ref{sec:experiments}.

After this, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal (Section \ref{sec:example_cases}). Specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).

% Antonio - CONCERN - The following section seems to be misplaced after moving the rest to Section 2. Thus, the Methodology Section is now a bit strange with just this subsection. We should think on moving this section and reorganize/improve the methodology description.

%-------------------------------------------------
\subsection{Data preprocessing by feature selection}
\label{subsec:data_preproces}

These FS techniques have been applied in the following section, including a comparison between all of them.

@@

@@

We have used both the {\tt CfsSubsetEval} (CSE) \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval (RFE) \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.

@@

Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
(numeric results can be seen in Tables 
\ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, 
\ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} 
in the appendix of tables).
Results in the figure show that the models performed similarly to the case of 
the global models for all publishers, which were previously presented in 
Figure \ref{fig:all_publishers_no_fs}. 
In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR. 
In the case of Best selling publisher houses (i.e. UDL929) and publishers who 
publish wide range of different books (i.e. UDL704), M5P could be recommended 
as it shows more accurate forecasting results than the other models. 
While in the case of medium sized publishers, in terms of sales and number 
of published books, the RF model would be adequate.

% tables have been moved to the Appendix and they have been substituted by the new Figure. Comments (text) have been adapted accordingly  -  [pedro]
%Tables \ref{Table:case1results}, \ref{Table:case2results}, \ref{Table:case3results} and \ref{Table:case4results}. 
%The results in these tables show that the classifiers performed similarly to the case of the global models for all publishers which were previously presented in Table \ref{tab:all_publishers_no_fs}. In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR. In the case of Best selling publisher houses (i.e. UDL929) and publishers who publish wide range of different books (i.e. UDL704), M5P could be recommended as it shows more accurate forecasting results than the other models. While in the case of medium sized publishers, in terms of sales and number of published books, the RF model would be adequate.

@@

In this stage of the experiments for the special cases, the
feature selection methods (RFE, CSE and SOM) are applied for each case
independently, since publishers with different sales ranges, and
targets, might in fact include different factors or have different
leverage when deciding how much to print.

@@

%  dejamos ésta finalmente: tablas al apéndice + incluimos nueva figura con los datos del RFE.
For clarity purpose, only obtained results after applying the RFE method for the 
four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}
 (detailed numeric results can be seen in 
Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, 
\ref{Table:case3results_fs_rf} and \ref{Table:case4results_fs_rf}
in the appendix of tables).
This one was chosen since the selected features by RFE method showed in the 
previous experiment the highest predictive power among all models.
As can be shown, RFE reduction has noticeably improved the performance of all 
classifiers specially in the case of the best selling publisher house (i.e. UDL929) 
and the publisher which publishes a wide range of different books (i.e. UDL704). 
For the rest of the results which are obtained by CSE and SOM feature selection 
methods we refer the reader to the appendix of tables at the end of this paper.

@@

Considering these datasets and the complete one, five machine learning
models for sales forecasting have been configured (according to the
problem requirements) and used to predict new book sales, from which
the optimal print-run could be estimated. These algorithms include
some based on Decision Trees (M5P and Random Forest), kNN, Support
Vector Machines and Linear Regression. 
These methods have been evaluated considering several performance
indicators (error measures) and also the time consumed to build the
corresponding models.

@@

Finally, there are some variables over which the publisher has some
control once the book has been published, such as the initial print-run, 
the books offered as gifts to reviewers, or what proportion is going to be sent 
to each possible point of sale. These can be incorporated into an optimisation 
model that will optimise those values to obtain desired sales.

>>>>

Our intention in this paper is to find out the main factors influencing
sales in order to create a \textit{tool} that the publisher can use to decide how many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a company that sells
software for publishers, we analyse them and compute predictive models that can be mainly used as decision-aid tools for book publishers. With these models, publishers will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book
sales, and, based on it, act consequently in order to maximize the books sold for a particular print run.

This will improve the current decision flow that the publishers follow, which consist in analysing (in a subjective way) the quality of the book and its features (author, genre, etc), and take a `fuzzy' decision roughly between printing 300 copies (standard book) or 5000 (best seller).

This process might be tedious, especially when the amount of data is quite large. Moreover, different experts can reach different predictions from the same dataset \cite{Sanders1994}.

With these issues in mind, in this paper, we firstly present an analysis on a real dataset, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}\\ Trevenque offers management systems and services for bookshops, publishers, and distributors}.
This study has been conducted by means of data mining and visualisation techniques. Then, a feature selection process is performed using three different methods, in order to find out what are the relevant variables describing a book  in the prediction, or estimation, procedure. 
% (Paloma) Why brackets? Suggestions:
% relevant variables describing a book in the prediction or regression procedure
% relevant variables describing a book in the prediction, or regression, procedure
% relevant variables describing a book in the prediction (regression) procedure <- here brackets are ok (me thinks)
% Antonio - I have chosen a better option for not repeating 'regression' in the following sentence
This procedure is performed by applying a set of regression algorithms to the different datasets (those with a different number of variables), yielding a set of models which could be used as the desired tool.

Given this, the main contribution of this paper to the state of the art is the development of the aforementioned methodology to process book sales data, in which: firstly, the most relevant variables are identified, and then, these variables are considered to `refine' the data in order to conduct accurate predictions on future sales. To our knowledge this is the first work in which regression methods have been applied to estimate sales for new launched books. Moreover, as stated before, we have used in the study a real dataset of book sales (related to the Spanish market), which is another point to remark.

The value of this methodology is contrasted considering four different
publishing companies being representative as top sellers, mid-range
sellers, the most varied, and one which sells a medium amount of
different books. From this, we draw insight on what are the important
factors when selling a book and some rule of thumbs extracted from the
prediction methods.

% (Paloma) From here:
%Usually, the company's expert sales managers analysed historical data
%and applied their knowledge on external variables to compute correct
%estimations (predictions); for instance, they can decide increasing or
%decreasing the sales forecast based on season or sales period. 
%Nevertheless, just carrying out the analysis and forecasting process
%as a human expert may lead to imprecise predictions, and they may not
%take all the variables into account.
% (Paloma) to here, is repeating all over again the process of deciding how many books to print. I think this paragraph should be unified somehow with the previous explanations and to re-order, because the previous paragraph seems like the end of the introduction, but then we go deep in the explanations again... It's not an easy read :(
% Antonio - removed and fused/reordered

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes, and shows a set of definitions of the regression methods applied in the paper as well as the evaluation metrics considered.
Then, Section \ref{sec:problem} introduces the problem of the estimation of print run
% (Paloma) Guys, 'print run' is written a total of 28 times:
% 23 are in the 'print-run' form
% 5 are 'print-run' (with a dash), of which one is inside the list of variables. But what about the rest inside text? Shouldn't they go ALL either with or without the dash?
% Antonio - I have replaced all of them by 'print run' as it seems to be the correct one
for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study.  These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies. Obtained results for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

@@

Thus, taking into account the kind of problem we address in this
paper, i.e. the prediction of sales of a new product for which no
historical data are available, the classical forecasting methods based
on time-series are not adequate, although they can obviously be used once 
the book has been launched for sale. 
In our work the relevant variables in the prediction of sales are identified
by means of data visualisation and feature selection methods. 
Then, machine learning techniques are applied to predict sales and to infer 
the ideal print run of a book.
In addition, since publishers need models to explain obtained predictions, 
`black box' forecasting methods may not be suitable, so models based
on decision rules have been tested as an alternative.

\begin{minipage}{2.45in}\begin{small}
 \begin{verbatim}
reference
author
retail price
subject1
subject2
subject3
publisher
collection
bookbinding
print run
total sales
dept stores sales
sales through delegates
rest of sales
total sales 1st year
mall sales 1st year
delegates sales 1st year
rest of sales 1st year
total distributed
distributed through dept stores
distributed through delegates
distributed - rest
total distributed 1st year
distrib. through dept stores 1st year
distrib. through delegates 1st year
\end{verbatim}
\end{small} \end{minipage}     &

Therefore, after the data has been \textit{collected} and initially \textit{preprocessed} (as described in the previous section), other preprocessing techniques have been applied, such as \textit{Feature Selection} (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.

FS methods check the relevance of all the variables of the patterns, aiming to reduce the set of features on a dataset, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
This task may also help to identify leading indicators to be considered 
by a human expert to make predictions.
At this stage of the methodology, both numerical and visualisation-based approaches have been applied, in order to select the best set of variables for the forecasting methods. These are described in Section \ref{subsec:fs_techniques}.

After this process has been conducted, different rule-based, tree-based and numerical \textit{forecasting methods} have been applied on the dataset. They are regression techniques and have been described in Section \ref{subsec:regression_methods}.

As a result of the previous step, several prediction models are obtained for the whole dataset. These have been \textit{evaluated} by means of the metrics described in Section \ref{subsec:evaluation_metrics}, and also \textit{analysed} in the experiments (Section \ref{sec:experiments}).

After this, the same methodology has been applied to some specific cases of publishing companies in order to \textit{validate} the proposal (Section \ref{sec:example_cases}). To this end, also specific interpretable models have been created as a final result of the work (Section \ref{subsec:decision_trees}).

In the following sections, the main techniques to be applied on these steps are described, along with the evaluation metrics computed to value the generated prediction models.

%-------------------------------------------------
\subsection{Feature selection techniques}
\label{subsec:fs_techniques}

These FS techniques have been applied in Section \ref{subsec:feature_selection}, including a comparison between all of them.

%-------------------------------------------------
\subsection{Regression methods}
\label{subsec:regression_methods}

As previously stated, there are many prediction algorithms available in the 
literature, each one with a different parameter set that may affect the 
obtained results.

@@

%-------------------------------------------------
\subsection{Evaluation metrics}
\label{subsec:evaluation_metrics}

@@

@@

It is important to note that both RF and M5P have an embedded feature selection mechanism (the variables which compose the final trees), however this is part of their inherent procedure. In the following section we will apply three filter-based feature selection techniques on the dataset, so all the methods will profit.

@@

We have used both the {\tt CfsSubsetEval} (CSE) \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval (RFE) \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:fs_techniques}.

@@

Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
(numeric results can be seen in Tables 
\ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, 
\ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} 
in the appendix of tables).

Results in the figure show that the models performed similarly to the case of 
the global models for all publishers, which were previously presented in 
Figure \ref{fig:all_publishers_no_fs}. 
In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR, and also better than MLP and ELM. Actually, the latter presents a low performance in these special cases (not previously for the whole dataset).
This could be due to the reported low robustness of the basic ELM version \cite{ding2015deep}, which we have applied in this work. More advanced versions such as the Multi-layer ELM, Hierarchical ELM and ELM with kernels will be investigated and experimented in the future work in order to reach better generalization performance.

In the case of Best selling publisher houses (i.e. UDL929) and publishers who 
publish wide range of different books (i.e. UDL704), M5P could be recommended 
as it shows more accurate forecasting results than the other models. 
While in the case of medium sized publishers, in terms of sales and number 
of published books, the RF model would be adequate.

@@

Now the feature selection methods (RFE, CSE and SOM) are applied for each case
independently, since publishers with different sales ranges, and targets, might in fact include different factors or have different leverage when deciding how much to print.

@@

For clarity purpose, only obtained results after applying the RFE method for the 
four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}.
Detailed numeric results of RFE on the special cases can be seen in 
Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, 
\ref{Table:case3results_fs_rf} and \ref{Table:case4results_fs_rf}
in the appendix of tables. 
RFE was chosen since the selected features by this method showed in the experiment with the whole dataset the highest predictive power among all models.
For the rest of the results which are obtained by CSE and SOM FS methods, we refer the reader also to the appendix of tables.

As it can be seen, RFE reduction has noticeably improved the performance of all 
classifiers specially in the case of the best selling publisher house (i.e. UDL929) and the one which publishes a wide range of different books (i.e. UDL704).

@@

Considering these datasets and the complete one, five machine learning
models for sales forecasting have been configured (according to the
problem requirements) and used to predict new book sales, from which
the optimal print run could be estimated. These algorithms include
some based on Decision Trees (M5P and Random Forest), kNN, Support
Vector Machines and Linear Regression. 
These methods have been evaluated considering several performance
indicators (error measures) and also the time consumed to build the
corresponding models.

@@

Finally, there are some variables over which the publisher has some
control once the book has been published, such as the initial print run, 
the books offered as gifts to reviewers, or what proportion is going to be sent 
to each possible point of sale. These can be incorporated into an optimisation 
model that will optimise those values to obtain desired sales.
